Downscaling coarse observations to predict continuous species spatio-temporal distribution

### 2022-05-23 Version_M2_plusieurszones/pres/RESSTE_2022/RESSTE_2022.Rmd
resste

---
\btVFill
\begin{center} \Large
\textbf{How to integrate all these datasources?}
\vspace{\baselineskip}
\large
(especially when they do not have the same spatial resolution)
\normalsize

\btVFill

\end{center}
\onslide<2>{
\normalsize
\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Some specific application in the context of fishery science: \\
\scriptsize
\textit{Alglave Baptiste, Rivot Etienne, Etienne Marie-Pierre, Woillez Mathieu, Thorson James T, Vermard Youen (2022). \textbf{Combining scientific survey and commercial catch data to map fish distribution.} ICES Journal of Marine Science IN PRESS. \url{https://doi.org/10.1093/icesjms/fsac032}}
\vspace{\baselineskip}
}

@@

\begin{table}
  \centering \scriptsize
  \begin{tabular}{ M{2cm} M{2cm} M{4cm} M{2cm} }
  \textcolor{BaptisteLightGreen}{\textbf{Alternative solution}} & 
  $\textcolor{BaptisteLightGreen}{D_j}=\sum_{\textcolor{BaptisteLightGreen}{i \in \mathcal{P}_j}}{Y_{i}}$          &
  $\textcolor{BaptisteLightGreen}{D_j} | \textcolor{BaptisteBlue}{S}_{\textcolor{BaptisteLightGreen}{\mathcal{P}_j}},\textcolor{BaptisteLightGreen}{\mathcal{P}_j} \sim \mathcal{L}_D( \textcolor{BaptisteBlue}{S}_{\textcolor{BaptisteLightGreen}{\mathcal{P}_j}},\xi,\sigma^2)$
  & \textcolor{BaptisteBlue}{\ding{224}}  Match $\mathcal{L}_D$ and $\mathcal{L}_Y$ moments \tiny (appendix) \\ 
  \end{tabular}
\end{table}

@@

@@

$$\operatorname{P}\left(D_j=d_{j} \vert d_j > 0 \right) = \quad \textbf{?}$$

@@

\textbf{Compute the moments}

@@

\textbf{Consider $D_j$ is Lognormal too}

@@

\item \textbf{ Change of support applications} \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Increasing amount of available data that may face such issues \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Here is one proposition to integrate aggregated data in SDM \\

>>>>

---
<!-- \btVFill -->
\begin{center} \Large
\textbf{How to integrate all these datasources?}
\end{center}
\large
(especially when they do not have the same spatial resolution)
\normalsize

\begin{block}{ \center \textbf{Change of support} }

\footnotesize
\textbf{Common issue in statistical literature} \vspace{\baselineskip}

\textbf{"Modifiable areal unit" problem (MAUP):} aggregation of data over increasingly larger geographic scales (e.g. data collected at point level but regrouped/declared at coarse level) \vspace{\baselineskip}

\textbf{Several fields of application:} climatology, health science, ecology \vspace{\baselineskip}

But mainly \textbf{standard observational data (Poisson, Gaussian)}, while data may be more complex in ecological applications (e.g. zero-inflated lognormal data)
\begin{center}
\textbf{\textcolor{BaptisteBlue}{\ding{224}} Objective of our work:} provide an approach that suits for complex data
\end{center}

\end{block}

\onslide<3>{
\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Base our model on an existing framework in the context of fishery science: \\
\tiny
\textit{Alglave Baptiste, Rivot Etienne, Etienne Marie-Pierre, Woillez Mathieu, Thorson James T, Vermard Youen (2022). \textbf{Combining scientific survey and commercial catch data to map fish distribution.} ICES Journal of Marine Science IN PRESS. \url{https://doi.org/10.1093/icesjms/fsac032}}
\vspace{\baselineskip}
}

@@

\begin{table}
  \centering \scriptsize
  \begin{tabular}{ M{2cm} M{2cm} M{4cm} M{2cm} }
  \textcolor{BaptisteLightGreen}{\textbf{Alternative solution}} & 
  $\textcolor{BaptisteLightGreen}{D_j}=\sum_{\textcolor{BaptisteLightGreen}{i \in \mathcal{P}_j}}{Y_{i}}$          &
  $\textcolor{BaptisteLightGreen}{D_j} | \textcolor{BaptisteBlue}{S}_{\textcolor{BaptisteLightGreen}{\mathcal{P}_j}},\textcolor{BaptisteLightGreen}{\mathcal{P}_j} \sim \mathcal{L}_D( \textcolor{BaptisteBlue}{S}_{\textcolor{BaptisteLightGreen}{\mathcal{P}_j}},\xi,\sigma^2)$
  & \textcolor{BaptisteBlue}{\ding{224}}  Match $\mathcal{L}_D$ and $\mathcal{L}_Y$ moments \\ 
  \end{tabular}
\end{table}

@@

\onslide<2>{

@@

$$\operatorname{P}\left(D_j=d_{j} \vert d_j > 0 \right) = \quad \textcolor{red}{\textbf{?}}$$

@@

\textbf{Compute the moments of $\mathbf{D_j\vert d_j > 0}$}

@@

\onslide<2>{

\textbf{Consider $\mathbf{D_j\vert d_j>0}$ is Lognormal too}

@@

\item \textbf{Moving to space-time ?} \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Extending the observation model to account for \textbf{temporal misalignment} \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Including spatio-\textbf{temporal covariance} in the latent field \\
